\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
	{\LARGE \textbf{Daniel Phang}}\\
	Seattle, Washington
	\vspace{0.05cm}
	\\
	\raisebox{-0.2\height} {\Large \faPhoneSquare} \ \  (000) 000-0000 \hfill\raisebox{-0.2\height}{\Large \faEnvelopeSquare} \ \ example@example.com \hfill \raisebox{-0.2\height}{\Large \faGithubSquare} \ \ github.com/example-profile \hfill \raisebox{-0.2\height}{\Large \faLinkedinSquare} \ \ linkedin.com/in/example
\end{center}

\hrule
\vspace{-1em}
\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
		
	\item
	      \headerrow
	      {\textbf{Microsoft}}
	      {\textbf{Redmond, WA}}
	      \headerrow
	      {\emph{Software Engineer II}}
	      {\emph{April 2019 -- Present}}
	      \begin{itemize*}
	      	\item Analyzed performance data and optimized legacy backend code for SharePoint Classic Publishing sites, improving query caching and CPU-heavy operations such as HTML rewriting.
	      	\item Designed and implemented quality-of-service dashboards and performance frameworks to dynamically detect performance issues across 400+ top companies.
	      	\item Improved data processing scripts that analyze daily site performance data for 1000+ companies, performance incidents, and engineering system health.
	      \end{itemize*}
	      	      
	\item
	      \headerrow
	      {\textbf{Amazon.com}}
	      {\textbf{Seattle, WA}}
	      \headerrow
	      {\emph{Software Development Engineer II}}
	      {\emph{October 2016 -- January 2019}}
	      \begin{itemize*}
	      	\item Designed and implemented ordering and accounting workflows to launch Prime Wardrobe US/UK/JP, a try-before-you-buy program for clothing, jewelry, and shoes.
	      	\item Reduced the US Prime Wardrobe non-payment rate significantly by implementing additional validations based on customer behavior patterns.
	      	\item Optimized Prime Wardrobe's Redshift cluster by intelligently distributing workloads, reducing peak CPU usage from 95\% to 50\% and peak disk usage from 90\% to 60\%.
	      	\item Migrated Prime Wardrobe's accounting backend to a next-generation plugin-based service, allowing for easy future integration with other retail programs.
	      \end{itemize*}
	      \headerrow
	      {\emph{Software Development Engineer I}}
	      {\emph{June 2014 -- October 2016}}
	      \begin{itemize*}
	      	\item Implemented critical detail page and globalized item publishing features to help launch the \emph{Rest of World} project, which enabled customers from 200+ countries to purchase digital software and video games.
	      	\item Designed and implemented an automated accounting solution for the Digital Software \& Video Games business, reducing the work required in monthly accounting close from 10+ hours to 2 hours.
	      	\item Created an internal Django website for vendor managers to manage pricing, blacklisting, and inventory for software and video games, reducing monthly operational time spent from 20+ hours to 10 hours.
	      \end{itemize*}
	      	      
	\item
	      \headerrow
	      {\textbf{Crunchyroll}}
	      {\textbf{San Francisco, CA}}
	      \headerrow
	      {\emph{Engineering Intern}}
	      {\emph{June 2013 -- August 2013}}
	      \begin{itemize*}
	      	\item Developed a new version of Crunchyroll’s application for the Roku platform.
	      	\item Worked with a designer to revamp the application’s user interface, improved HD video playback, and implemented a multilingual translations framework.
	      \end{itemize*}
	      	      
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Skills}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
	\item \textbf{Languages:}
	      C\#, HTML/CSS, Java, JavaScript, \LaTeX, Python, SQL
	\item \textbf{Software:}
	      Atlassian (Bitbucket, Jira, Confluence), AWS (DynamoDB, EC2, Lambda, RDS, Redshift, S3, SQS), Microsoft (Azure DevOps, Visual Studio), DigitalOcean, Django, Heroku, IntelliJ IDEA, Selenium
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{Lehigh University}}
	      {\textbf{Bethlehem, PA}}
	      \headerrow
	      {\emph{M.S. Computer Science} (\textbf{GPA:} 3.96/4.00)}
	      {\emph{August 2013 -- May 2014}}
	      \headerrow
	      {\emph{B.S. Computer Engineering (Minor in Economics)} (\textbf{GPA:} 3.77/4.00)}
	      {\emph{August 2009 -- May 2013}}
	      	      
\end{itemize}

\end{document}
